---
title: "SNPassoc: an R package to perform whole genome association studies"
author: "Juan R. Gonzalez, Victor Moreno"
date: "`r Sys.Date()`"
package: "`r pkg_ver('SNPassoc')`"
output: 
  BiocStyle::pdf_document
vignette: >
  %\VignetteIndexEntry{SNPassoc: an R package to perform whole genome association studies}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8} 
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

# Introduction

The `SNPassoc` package contains facilities for data manipulation, tools for exploratory data analysis, convenient graphical facilities, and tools for assessing genetic association for both quantitative and categorial (case-control) traits in whole genome approaches. Genome-based studies are normally analyzed using a multistage approach. In the first step researchers are interested in assessing association between the outcome and thousands of SNPs. In a second and possibly third step, medium/large scale studies are performed in which only a few hundred of SNPs, those with a putative association found in the first step, are genotyped. `SNPassoc` is specially designed for
analyzing this kind of designs. In addition, a convenience-based approach (select variants on the basis of logistical considerations such as the ease and cost of genotyping) can also be analyzed using `SNPassoc`. Different genetic models are
also implemented in the package. Analysis of multiple SNPs can be analyzed using either haplotype or gene-gene interaction approaches. Statistical methods implemented in the functions are briefly described by the end of this report as well as some computational aspects.


# Data manipulation and descriptive analysis

To be supplied


```{r}
sessionInfo()
```

